A basis for selecting light spectral distribution for evaluating leaf photosynthetic rates of plants grown under different light spectral distributions

### 2016-08-26 Header.Rmd
AcknowledgementにEWを追加。
no message

output:
#   pdf_document:
#     latex_engine: xelatex
#     fig_caption: TRUE
  html_document:
    toc: TRUE
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: TRUE
  # word_document:
  #   toc: FALSE
    # fig_caption: TRUE
---

@@

>>>>

output:
#   pdf_document:
#     latex_engine: xelatex
#     fig_caption: TRUE
  # html_document:
  #   toc: TRUE
  #   depth: 3
  #   theme: sandstone
  #   self_contained: TRUE
  #   fig_caption: TRUE
  word_document:
    toc: FALSE
  fig_caption: TRUE
---

@@

**Acknowledgements**

  We thank Dr. Sander W. Hogewoning (Plant Lighting B.V., The Netherlands) and Dr. Emilie Wientjes (Wageningen University, The Netherlands) for providing data of absorbance spectra of photosystems.
  This work was supported by JSPS KAKENHI Grant Number 26·9372.
